---
title: "Untitled"
output: ''
---

Load different packages that will use in this model:

```{r}
pkg_list = c("ggplot2","plyr")
mia_pkgs = pkg_list[!(pkg_list %in% installed.packages()[,"Package"])]
if(length(mia_pkgs) > 0) install.packages(mia_pkgs)
loaded_pkgs = lapply(pkg_list, require, character.only=TRUE)
```

Set up the data:
```{r}
jdata = read.csv("datarelatedjobs.csv")
names(jdata)
length(jdata$Standing)
```

An overview of job data:

```{r}
summary(jdata)
head(jdata)
```

Comparing between companies in the North and the South of California (using side-by-side histogram):

- Number of companies in North vs South
- Number of Bachelor's, Master's, Ph.D that companies recruiting in North vs South. (All levels = add 1 to every value)
- Average salary in North vs South

```{r}
bache = rep(0, 400)
mastr = rep(0, 400)
phd   = rep(0, 400)
count(jdata$Standing)
git config --global user.email "you@example.com"
git config --global user.name "Your Name"
```

Plot a histogram to see the prefer language for both prefer language 1 and prefer language 2



Write function to find out suitable companies: "find_company" that has 4 agrument. Minimum standing, experience, region, best language. It will return the dataframe that has all the company that fit our agruments


